---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# ppitables: Lookup tables to generate poverty likelihoods and rates using the Poverty Probability Index (PPI)
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)
[![CRAN](https://img.shields.io/cran/v/ppitables.svg)](https://CRAN.R-project.org/package=ppitables)
[![CRAN](https://img.shields.io/cran/l/ppitables.svg)](https://github.com/validmeasures/ppitables/blob/master/LICENSE.md)
[![CRAN](http://cranlogs.r-pkg.org/badges/ppitables)](https://CRAN.R-project.org/package=ppitables)
[![Travis-CI Build Status](https://travis-ci.org/validmeasures/ppitables.svg?branch=master)](https://travis-ci.org/validmeasures/ppitables)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/validmeasures/ppitables?branch=master&svg=true)](https://ci.appveyor.com/project/validmeasures/ppitables)

Lookup tables for estimating the likelihood of poverty using the `Poverty Probability Index` (previously called `Progress out of Poverty Index`) or `PPI` from country-specific indicators collected from cross-sectional surveys. This lookup table is extracted from documentation of the `PPI` found at [https://www.povertyindex.org](https://www.povertyindex.org).


## Installation

You can install `ppitables` from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("validmeasures/ppitables")
library(ppitables)

```


## Usage

The `ppitables` package contains PPI lookup tables for 60 countries. To be able to use the tables in the `ppitables` appropriately, you need to be aware of the naming syntax used for the tables for each country. The name for each table starts with `ppiMatrix` followed by the three letter ISO code of the country of interest. So, for example, you can access the PPI table for Bangladesh with:

```{r usage, eval = FALSE}
# call PPI table for Bangladesh (ISO code - BGD)
# install.packages("washdata")
library(ppitables)
ppiMatrixBGD
```

Some PPI country table names are suffixed to indicate that they refer to either a newer version of the lookup table for the particular country, or a more localised table using country-specific poverty cutoffs.

Following are the available PPI country tables from the `ppitables` package. This is updated as at 14 February 2018 using information from the PPI [site](https://www.povertyindex.org).


### List of PPI country tables

+-----------------------------+-----------------------------------------------------+
| **PPI Country Table Name**  |  **Description**                                    |
+=============================+=====================================================+
| 1. `ppiMatrixAFG`           | PPI for Afghanistan based on 2007/8 National Risk   |
|                             | and Vulnerability Survey (NRVA)                     |
+-----------------------------+-----------------------------------------------------+
| 2. `ppiMatrixAGO`           | PPI for Angola based on the 2008/2009 Household     |
|                             | Living Standards Survey                             |
+-----------------------------+-----------------------------------------------------+
| 3. `ppiMatrixBEN`           | PPI for Benin based on 2010 data                    |
+-----------------------------+-----------------------------------------------------+
| 4. `ppiMatrixBFA`           | PPI for Burkina Faso using Burkina Faso’s 2014      |
|                             | Enquête Multisectorielle Continue (EMC) Survey      |
+-----------------------------+-----------------------------------------------------+
| 5. `ppiMatrixBGD`           | PPI for Bangladesh using Bangaldesh's 2010 HIES     |
|                             | Survey                                              |
+-----------------------------+-----------------------------------------------------+
| 6. `ppiMatrixBOL`           | PPI for Bolivia using Bolivia’s 2013 Household      |
|                             | Survey                                              |
+-----------------------------+-----------------------------------------------------+
| 7. `ppiMatrixBRA`           | PPI for Brazil based on the 2008 PNAD               |
+-----------------------------+-----------------------------------------------------+
| 8. `ppiMatrixCIV`           | PPI for Ivory Coast using the Ivory Coast's 2008    |
|                             | Household Living Standards Survey                   |
+-----------------------------+-----------------------------------------------------+
| 9. `ppiMatrixCMR`           | PPI for Cameroon using Cameroon’s 2007 Household    |
|                             | Survey                                              |
+-----------------------------+-----------------------------------------------------+
|10. `ppiMatrixCOL`           | PPI for Colombia based on Colombia’s 2009 Encuesta  |
|                             | Integrada de Hogares. This table uses the legacy    |
|                             | poverty cutoffs.                                    |
+-----------------------------+-----------------------------------------------------+
|    `ppiMatrixCOL_a`         | PPI for Colombia based on Colombia's 2009 Encuesta  |
|                             | Integrada de Hogares. This table uses the new       |
|                             | poverty cutoffs for Colombia.                       |
+-----------------------------+-----------------------------------------------------+
| 11. `ppiMatrixDOM`          | PPI for Dominican Republic based on the 2007        |
|                             | Encuesta Nacional de Ingresos y Gastos de los       |
|                             | Hogares (ENIGH)                                     |
+-----------------------------+-----------------------------------------------------+
| 12. `ppiMatrixEGY`          | PPI for Egypt based on the 2004/5 HIECS             |
+-----------------------------+-----------------------------------------------------+
| 13. `ppiMatrixETH`          | PPI for Ethiopia based on Ethiopia’s 2010/11        |
|                             | Household Consumption and Expenditure Survey        |
+-----------------------------+-----------------------------------------------------+
| 14. `ppiMatrixFJI`          | PPI for Fiji based on Fiji’s 2008/9 Household Income| 
|                             | and Expenditure Survey                              |
+-----------------------------+-----------------------------------------------------+
| 15. `ppiMatrixGHA`          | PPI for Ghana based on Ghana’s 2012/13 Living       |
|                             | Standards Survey using legacy poverty lines         |
+-----------------------------+-----------------------------------------------------+
|     `ppiMatrixGHA_a`        | PPI for Ghana based on Ghana’s 2012/13 Living       |
|                             | Standards Survey using the new-definition poverty   |
|                             | lines deflated with Ghana's CPI                     |
+-----------------------------+-----------------------------------------------------+
|     `ppiMatrixGHA_b`        | PPI for Ghana based on Ghana’s 2012/13 Living       |
|                             | Standards Survey using the new-definition poverty   |
|                             | lines deflated with the change in 100% of national  |
|                             | poverty line                                        |
+-----------------------------+-----------------------------------------------------+
| 16. `ppiMatrixGTM`          | PPI for Guatemala based on Guatemala’s 2014         |
|                             | Household Living Standards Survey                   |
+-----------------------------+-----------------------------------------------------+
| 17. `ppiMatrixHND`          | PPI for Honduras based on the 2007 EPHPM            |
+-----------------------------+-----------------------------------------------------+
| 18. `ppiMatrixHTI`          | PPI for Haiti based on Haiti’s 2012 Post-Earthquake |
|                             | Living Standards Survey                             |
+-----------------------------+-----------------------------------------------------+
| 19. `ppiMatrixIDN`          | PPI for Indonesia based on data from 2010 using     |
|                             | legacy poverty lines                                |
+-----------------------------+-----------------------------------------------------+
|     `ppiMatrixIDN`          | PPI for Indonesia based on data from 2010 using new | 
|                             | definition poverty lines                            |
+-----------------------------+-----------------------------------------------------+
| 20. `ppiMatrixIND_r59`      | PPI for India using India’s 2011/12 Socio-Economic  |
|                             | using the R59 legacy poverty lines using MRP        |
|                             | consumption                                         |
+-----------------------------+-----------------------------------------------------+
|     `ppiMatrixIND_r62`      | PPI for India using India’s 2011/12 Socio-Economic  |
|                             | using the R59 legacy poverty lines using MRP        |
|                             | consumption                                         |
+-----------------------------+-----------------------------------------------------+
|     `ppiMatrixIND_r66`      | PPI for India using India’s 2011/12 Socio-Economic  |
|                             | using the R66 legacy poverty lines using MRP        |
|                             | consumption                                         |
+-----------------------------+-----------------------------------------------------+
|     `ppiMatrixIND_r68`      | PPI for India using India’s 2011/12 Socio-Economic  |
|                             | using the R68 new poverty lines using MRP           |
|                             | consumption                                         |
+-----------------------------+-----------------------------------------------------+
| 21. `ppiMarixJOR`           | PPI for Jordan using Jordan’s 2006 Household Income |
|                             | and Expenditure Survey                              |
+-----------------------------+-----------------------------------------------------+
| 22. `ppiMatrixKEN`          | PPI for Kenya using Kenya’s 2005/06 Integrated      |
|                             | Household Budget Survey                             |
+-----------------------------+-----------------------------------------------------+
| 23. `ppiMatrixKGZ`          | PPI for Kyrgyzstan Kyrgyz Republic’s 2012 Integrated|
|                             | Household Survey                                    |
+-----------------------------+-----------------------------------------------------+
| 24. `ppiMatrixKHM`          | PPI for Cambodia using Cambodia’s 2011              |
|                             | Socio-Economic Survey based using legacy poverty    |
|                             | lines                                               |
+-----------------------------+-----------------------------------------------------+
|     `ppiMatrixKHM_gov`      | PPI for Cambodia using Cambodia’s 2011              |
|                             | Socio-Economic Survey based using government        |
|                             | definition poverty lines                            |
+-----------------------------+-----------------------------------------------------+
|     `ppiMatrixKHM_wb`       | PPI for Cambodia using Cambodia’s 2011              |
|                             | Socio-Economic Survey based using World Bank        |
|                             | definition poverty lines                            |
+-----------------------------+-----------------------------------------------------+
| 25. `ppiMatrixLKA`          | PPI for Sri Lanka using Sri Lanka’s 2012/13         |
|                             | Household Income and Expenditure Survey             |
+-----------------------------+-----------------------------------------------------+
| 26. `ppiMatrixMAR`          | PPI for Morocco based on Morocco’s 2007 Households  |
|                             | Living Standards Survey                             |
+-----------------------------+-----------------------------------------------------+
| 27. `ppiMatrixMDG`          | PPI for Madagascar based on Madagascar’s 2010       |
|                             | Periodic Household Survey                           |
+-----------------------------+-----------------------------------------------------+
| 28. `ppiMatrixMEX`          | PPI for Mexico based on Mexico's Encuesta Nacional  |
|                             | de Ingresos y Gastos de los Hogares de 2014 using   |
|                             | legacy definitions of poverty                       |
+-----------------------------+-----------------------------------------------------+
|     `ppiMatrixMEX_a`        | PPI for Mexico based on Mexico's Encuesta Nacional  |
|                             | de Ingresos y Gastos de los Hogares de 2014 using   |
|                             | new definitions of poverty                          |
+-----------------------------+-----------------------------------------------------+
| 29. `ppiMatrixMLI`          | PPI for Mali based on Mali's 2001 Poverty Evalution |
|                             | Survey                                              |
+-----------------------------+-----------------------------------------------------+
| 30. `ppiMatrixMMR`          | PPI for Myanmar based on Myanmar’s 2009/10          |
|                             | Integrated Household Living Conditions Assessment   |
+-----------------------------+-----------------------------------------------------+
| 31. `ppiMatrixMNG`          | PPI for Mongolia based on Mongolia’s 2014 Household |
|                             | Socio-Economic Survey                               |
+-----------------------------+-----------------------------------------------------+
| 32. `ppiMatrixMOZ`          | PPI for Mozambique based on 2008/9 Household Budget |
|                             | Survey                                              |
+-----------------------------+-----------------------------------------------------+
| 33. `ppiMatrixMWI`          | PPI for Malawi based on Malawi's 2010/11 Integrated |
|                             | Household Survey using legacy poverty definitions   |
+-----------------------------+-----------------------------------------------------+
|     `ppiMatrixMWI_gov`      | PPI for Malawi based on Malawi's 2010/11 Integrated |
|                             | Household Survey using government poverty           |
|                             | definitions                                         |
+-----------------------------+-----------------------------------------------------+
|     `ppiMatrixMWI_pbm`      | PPI for Malawi based on Malawi's 2010/11 Integrated |
|                             | Household Survey using PBM poverty definitions      |
+-----------------------------+-----------------------------------------------------+
| 34. `ppiMatrixNAM`          | PPI for Namibia based on Namibia’s 2009/10 Household|
|                             | Income and Expenditure Survey                       |
+-----------------------------+-----------------------------------------------------+
| 35. `ppiMatrixNER`          | PPI for Niger based on Niger’s 2007/8 National      |
|                             | Household Budget and Expenditure Survey             |
+-----------------------------+-----------------------------------------------------+
| 36. `ppiMatrixNGA`          | PPI for Nigeria based on Nigeria’s 2012/13 General  |
|                             | Household Panel Survey                              |
+-----------------------------+-----------------------------------------------------+
| 37. `ppiMatrixNIC`          | PPI for Nicaragua based on Nicaragua’s 2009 Living  |
|                             | Standards Measurement Survey                        |
+-----------------------------+-----------------------------------------------------+
| 38. `ppiMatrixNPL`          | PPI for Nepal using legacy poverty definition lines |
+-----------------------------+-----------------------------------------------------+
|     `ppiMatrixNPL_a`        | PPI for Nepal using new poverty definition lines    |
+-----------------------------+-----------------------------------------------------+
| 39. `ppiMatrixPER`          | PPI for Peru based on Peru’s 2010 National Household|
|                             | Survey                                              |
+-----------------------------+-----------------------------------------------------+
| 40. `ppiMatrixPHL`          | PPI for the Philippines based on Philippines 2009   |
|                             | FIES/LFS.                                           |
+-----------------------------+-----------------------------------------------------+
| 41. `ppiMatrixPRY`          | PPI for Paraguay based on Paraguay’s 2011 EPH       |
+-----------------------------+-----------------------------------------------------+
| 42. `ppiMatrixPSE`          | PPI for Palestine based on Palestine's 2011         |
|                             | Expenditure and Consumption Survey                  |
+-----------------------------+-----------------------------------------------------+
| 43. `ppiMatrixROU`          | PPI for Romania based on the 2007 HBS               |
+-----------------------------+-----------------------------------------------------+
| 44. `ppiMatrixRUS`          | PPI for Russia based on 2007 HBS                    |
+-----------------------------+-----------------------------------------------------+
| 45. `ppiMatrixRWA`          | PPI for Rwanda based on Rwanda’s 2010/11 Integrated |
|                             | Household Living Standards Survey                   |
+-----------------------------+-----------------------------------------------------+
| 46. `ppiMatrixSEN`          | PPI for Senegal based on Senegal's 2005/6 Enquête de|
|                             | Suivi de la Pauvreté au Sénégal (ESPS)              |
+-----------------------------+-----------------------------------------------------+
| 47. `ppiMatrixSLE`          | PPI for Sierra Leone based on Sierra Leone's 2003/4 |
|                             | HIS                                                 |
+-----------------------------+-----------------------------------------------------+
| 48. `ppiMatrixSLV`          | PPI for El Salvador based on the 2008 EHPM          |
+-----------------------------+-----------------------------------------------------+
| 49. `ppiMatrixSYR`          | PPI for Syria based on Syria's 2006/7 Household     |
|                             | Income and Expenditure Survey                       |
+-----------------------------+-----------------------------------------------------+
| 50. `ppiMatrixTJK`          | PPI for Tajikistan based on 2007 data               |
+-----------------------------+-----------------------------------------------------+
| 51. `ppiMatrixTLS`          | PPI for Timor Leste based on Timor-Leste’s 2007     |
|                             | Survey of Living Standards                          |
+-----------------------------+-----------------------------------------------------+
| 52. `ppiMatrixTZA`          | PPI for Tanzania based on Tanzania’s 2011/12        |
|                             | Household Budget Survey                             |
+-----------------------------+-----------------------------------------------------+
| 53. `ppiMatrixUGA`          | PPI for Uganda based on Uganda's 2012/13 National   |
|                             | Household Survey                                    |
+-----------------------------+-----------------------------------------------------+
| 54. `ppiMatrixVNM`          | PPI for Vietnam based on the 2006 VHLSS             |
+-----------------------------+-----------------------------------------------------+
| 55. `ppiMatrixYEM`          | PPI for Yemen based on 2005/06 HBS                  |
+-----------------------------+-----------------------------------------------------+
| 56. `ppiMatrixZAF`          | PPI for South Africa based on the 2005/6 IES        |
+-----------------------------+-----------------------------------------------------+
| 57. `ppiMatrixZMB`          | PPIi for Zambia based on Zambia’s 2015 Living       |
|                             | Conditions Monitoring Survey (LCMS)                 |
+-----------------------------+-----------------------------------------------------+






