---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# ppitables: Lookup tables to generate poverty likelihoods and rates using the Poverty Probability Index (PPI)
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)
[![CRAN](https://img.shields.io/cran/v/ppitables.svg)](https://CRAN.R-project.org/package=ppitables)
[![CRAN](https://img.shields.io/cran/l/ppitables.svg)](https://github.com/validmeasures/ppitables/blob/master/LICENSE)
[![CRAN](http://cranlogs.r-pkg.org/badges/ppitables)](http://cran.rstudio.com/web/packages/ppitables/index.html)
[![Travis-CI Build Status](https://travis-ci.org/validmeasures/ppitables.svg?branch=master)](https://travis-ci.org/validmeasures/ppitables)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/validmeasures/ppitables?branch=master&svg=true)](https://ci.appveyor.com/project/validmeasures/ppitables)

Lookup tables for estimating the likelihood of poverty using the `Poverty Probability Index` (previously called `Progress out of Poverty Index`) or `PPI` from country-specific indicators collected from cross-sectional surveys. This lookup table is extracted from documentation of the `PPI` found at [https://www.povertyindex.org](https://www.povertyindex.org).


## Installation

You can install `ppitables` from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("validmeasures/ppitables")
```
